\begin{enumerate}[(a)]
    \item Let $G$ be an outerplanar graph. We then add a vertex $v$ 
    that is adjacent to all vertices in $G$. 
    
    We can see this graph $G+v$ is planar by drawing $v$
    above the embedding of $G$ and joining $v$ with the vertices in $G$ 
    along the outer boundary. These edges don't cross any boundaries of 
    $G$ so $G+v$ is planar.  $G+v \cong G+K_1$.

    Let $G$ not be outerplanar and let $G+K_1$ be planar. We can embed
    $G+K_1$ so that $K_1$ is on the outer boundary of $G+K_1$.
    If we remove $K_1$ from this embedding there should exist a
    vertex $a$ on the interior of $G$ since $G$ is not outerplanar.
    But then the edge $aK_1$ crosses an edge on the outer boundary
    of $G$ making $G+K_1$ not planar, contradiction. Therefore
    $G$ is outerplanar.

    \item Let $G$ be an outerplanar graph of order $n \ge 2$ and size $m$, 
    then $G+K_1$ is planar with size $m+n$ and order $n+1$. Then
    by Corollary 33 
        $$ m+n \le 3(n+1) - 6 = 3n+3-6 = 3n-3$$
        $$m \le 2n-3$$
        as required.

    \item $G$ is outerplanar iff $G+K_1$ is planar iff $G+K_1$ contains
			a subdivision of
			$K_5$ or $K_{3,3}$ (Kuratowski). We show
			this is equivalent to $G$ containing a subdivision of $K_4$ or $K_{2,3}$.

			Let $v$ be the vertex of $K_1$, and suppose $G+K_1$ contains $S$,
			a subdivision of $K_5$ or $K_{3,3}$. If $v \notin S$, then
			$G$ contains a subdivision of $K_5$ or $K_{3,3}$ , so contains
			a subdivision of $K_4$ or $K_{2,3}$. Otherwise $v \in S$.
			But then $S-v$ still contains a subdivision of $K_4$ or $K_{2,3}$,
			since if $P$ is $K_5$ or $K_{3,3}$ minus any vertex or edge,
			$P$ still contains $K_4$ or $K_{2,3}$ as a subgraph, respectively.
			Since $S-v$ is a subgraph of $G$, $G$ contains a subdivision of 
			$K_4$ or $K_{2,3}$. 

			Now suppose $G$ contains $S$, a subdivision of $K_4$ or $K_{2,3}$.
			Then $S+K_1$ contains a subdivision of $K_5$ or $K_{3,3}$, but
			$S+K_1$ is a subgraph of $G+K_1$, so $G+K_1$ contains a subdivision of 
			$K_5$ or $K_{3,3}$ .
\end{enumerate}
